\begin{proof}
  \begin{itemize}
    \item ($\Leftarrow$) Suppose that
    \begin{equation}
      \label{conv:proof:rev}
      \rounds - 1 \geq \left(\postlen - 1\right)\ceil*{\frac{a+b}{\regen}}
      \enspace.
    \end{equation}
    Let $\pid \in \left[\playerlen\right]$. In this case it is $\rounds \geq
    \postlen$ and according to \textsc{VoteThisRound} in
    Algorithm~\ref{alg:steem:vote}, $u_{\pid}$ votes non-null in rounds
    $\left(\round_1, \dots, \round_\postlen\right)$ with $r_i = \floor*{\left(i
    - 1\right)\frac{\rounds - 1}{\postlen - 1}} + 1$. Observe that:
    \begin{gather}
      \label{conv:proof:integer}
      \left(\ref{conv:proof:rev}\right) \Rightarrow \frac{\rounds - 1}{\postlen
      - 1} \geq \ceil*{\frac{a+b}{\regen}}
      \underset{\text{integer}}{\overset{\text{rhs}}{\Rightarrow}}
      \floor*{\frac{\rounds - 1}{\postlen - 1}} \geq \ceil*{\frac{a+b}{\regen}}
      \enspace, \\
      \label{conv:proof:step}
      \forall i \in \left[\postlen\right] \setminus \left\{1\right\}, r_i
      \in \left\{r_{i - 1} + \floor*{\frac{\rounds - 1}{\postlen - 1}}, r_{i -
      1} + \ceil*{\frac{\rounds - 1}{\postlen - 1}}\right\} \enspace.
    \end{gather}
    From (\ref{conv:proof:integer}) and (\ref{conv:proof:step}) we have that
    $\forall i \in \left[\postlen - 1\right], r_{i+1} - r_i \geq
    \ceil*{\frac{a+b}{\regen}}$. We will now prove by induction that $\forall i
    \in \left[\postlen\right], \votpowvec_{\pid, r_i} = 1$.

    \begin{itemize}
      \item For $i = 1, \votpowvec_{\pid, 1} = 1$
      (Algorithm~\ref{alg:steem:init}, line~\ref{alg:steem:init:vp}).
      \item Let $\votpowvec_{\pid, r_i} = 1$. Until $r_{i + 1}$, a single
      non-null vote is cast by $u_\pid$, which reduces $\votpowvec_{\pid}$ by at
      most $a + b$ (Algorithm~\ref{alg:steem:handlevote},
      line~\ref{alg:steem:handlevote:cost:start}) and at least $\ceil*{\frac{a +
      b}{\regen}}$ regenerations, each of which replenishes $\votpowvec_{\pid}$
      by $\regen$. Thus
      \begin{equation*}
        \votpowvec_{\pid, r_{i + 1}} \geq \min{\left\{\votpowvec_{\pid, r_i} - a
        - b + \regen\ceil*{\frac{a + b}{\regen}}, 1\right\}} \geq 1 \enspace.
      \end{equation*}
      But $\votpowvec_{\pid}$ cannot exceed 1
      (line~\ref{alg:steem:handlevote:regen}), thus $\votpowvec_{\pid, r_{i +
      1}} = 1$.
    \end{itemize}
    Since the above holds for every $\pid \in \left[\playerlen\right]$, it holds
    that at the end of the execution, all votes have been cast with full voting
    power, thus $\forall i \in \left[\postlen\right],
    \mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) =
    \playerlen b + a \sum\limits_{\pid = 1}^\playerlen
    \postlist\left[i\right]_{\pid}$ and the posts in $\postlist_R$ are sorted by
    decreasing score (Algorithm~\ref{alg:steem:handlevote},
    line~\ref{alg:steem:handlevote:order}). We observe that
    \begin{gather*}
      \forall i \neq j \in \left[\postlen\right], \idsc{\postlist\left[i\right]}
      > \idsc{\postlist\left[j\right]} \Rightarrow \\
      \sum\limits_{\pid = 1}^\playerlen \postlist\left[i\right]_\pid >
      \sum\limits_{\pid = 1}^\playerlen \postlist\left[j\right]_\pid \Rightarrow
      \\
      \playerlen b + a \sum\limits_{\pid = 1}^\playerlen
      \postlist\left[i\right]_\pid > \playerlen b + a \sum\limits_{\pid =
      1}^\playerlen \postlist\left[j\right]_\pid \enspace.
    \end{gather*}
    Thus all posts will be ordered according to their ideal scores; put
    otherwise, $\textsc{IdealScore}^M\left(\postlist_\rounds\right)$ holds.

%   \item ($\stpowvec$ variable $\Rightarrow$ no convergence) Let $\postlist =
%   \left[\left(1, \left(a_1, \dots, a_\playerlen\right)\right), \left(1,
%   \left(b_1, \dots, b_\playerlen\right)\right), \left(1, \left(0, \dots,
%   0\right)\right), \dots, \left(1, \left(0, \dots, 0\right)\right)\right]$
%   such that the following linear constraints are simultaneously feasible:
%   \begin{gather*}
%     \sum\limits_{i=1}^\playerlen a_i > \sum\limits_{i=1}^\playerlen b_i \\
%     \sum\limits_{i=1}^\playerlen \stpow_i a_i < \sum\limits_{i=1}^\playerlen
%     \stpow_i  b_i
%   \end{gather*}
%   I think that's always possible if $\stpow$ is not constant.
%
    \item ($\Rightarrow$) Suppose that
    \begin{equation}
      \label{conv:proof:fewrounds}
      \rounds - 1 < \left(\postlen - 1\right)\ceil*{\frac{a+b}{\regen}}
      \enspace.
    \end{equation}

    Several lists of posts will be defined in the rest of the proof. Given that,
    when all players are honest, the creator of a post is irrelevant, we omit
    the creator from the definition of posts to facilitate the exposition. Thus
    every post will be defined as a tuple of likabilities.

    First, we consider the case when
    \begin{equation}
      \label{conv:proof:smallattspanrounds}
      \attspan + \rounds \leq \postlen \enspace.
    \end{equation}
    In this case, no player can ever vote for the last post, as we will show
    now. First of all, $(\ref{conv:proof:smallattspanrounds}) \Rightarrow
    \rounds < \postlen$, thus all players cast $\rounds$ votes in total. Let
    $\pid \in \playerlen, i \in \left[\rounds\right]$ and $v_{\pid, i}$ the
    index of the last post that has ever been in $\player_\pid$'s attention
    span until the end of round $i$, according to the ordering of $\postlist$.
    It is $v_{\pid, 1} = \attspan$ and $\forall i \in \left[\rounds\right]
    \setminus \left\{1\right\}, v_{\pid, i} = v_{\pid, i - 1} + 1$, since in
    every round $\player_\pid$ votes for a single post and the first unvoted
    post of the list is added to their attention span. Note that, since this
    mechanism is the same for all players, the same unvoted post is added to
    all players' attention span at every round. Thus $\forall \pid \in
    \playerlen, v_{\pid, \rounds} = \attspan + \rounds - 1
    \overset{\left(\ref{conv:proof:smallattspanrounds}\right)}{<} \postlen$.
    We deduce that no player has ever the chance to vote for the last post.

    The above observation naturally leads us to the following counterexample:
    Let
    \begin{gather*}
      \strongpost = \left(\underbrace{1, \dots, 1}_{\playerlen}\right) \\
      \nullpost = \left(\underbrace{0, \dots, 0}_{\playerlen}\right) \\
      \postlist = \left[\underbrace{\nullpost, \dots, \nullpost}_{\postlen -
      1}, \strongpost\right]
    \end{gather*}

    $\forall i \in \left[\postlen - 1\right],$ it is
    $\idsc{\postlist\left[\postlen\right]} >
    \idsc{\postlist\left[\postlen\right]}$, thus $\forall \postlist'$ that
    contain the same posts as $\postlist$ and
    $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[\postlen\right]$. However,
    since the last post is not voted by any player and the first post is voted
    by at least one player, it is
    $\mathrm{sc}_\rounds\left(\postlist\left[1\right]\right) >
    \mathrm{sc}_\rounds\left(\postlist\left[\postlen\right]\right)$, thus
    $\textsc{Ideal}^1\left(\postlist_\rounds\right)$ does not hold.

    We now move on to the case when $\attspan + \rounds > \postlen$. Let
    $\votenum = \min{\left\{\rounds, \postlen\right\}}$. Each player casts
    exactly $\votenum$ votes. Consider $\postlist^1 = 1^{\postlen \times
    \playerlen}$ and $\pid \in \left[\playerlen\right]$. Let
    \begin{equation*}
      i \in \left[\votenum\right] :\left(\votpowvecreg_{\pid, \round_i} < 1
      \wedge \nexists i' < i: \votpowvecreg_{\pid, \round_{i'}} < 1\right)
      \enspace,
    \end{equation*}
    i.e. $i$ is the first round in which $u_\pid$ votes with less than full
    voting power. Such a round exists in every case as we will show now. Note
    that, since the first round is a voting round and the voting power of all
    players is full at the beginning, if $i$ exists it is $i \geq 2$.

    \begin{itemize}
      \item If $\rounds \geq \postlen$, it is $\votenum = \postlen$. \\
      If $\nexists i \in \left[\postlen\right] :\left(\votpowvecreg_{\pid,
      \round_i} < 1 \wedge \nexists i' < i: \votpowvecreg_{\pid, \round_{i'}} <
      1\right)$, then $\forall i \in \left[\postlen\right], \votpowvecreg_{\pid,
      \round_i} = 1 \Rightarrow \forall i \in \left[\postlen\right] \setminus
      \left\{1\right\}, \round_i \geq \round_{i - 1} + \ceil*{\frac{a +
      b}{\regen}}$ to have enough rounds to replenish the voting power after a
      full-weight, full-voting power vote. Thus $\round_\postlen \geq 1 +
      \left(\postlen - 1\right)\ceil*{\frac{a + b}{\regen}} > \rounds$,
      contradiction.

      \item If $\rounds < \postlen$, every player votes on all rounds, thus $r_2
      = 2$. Note that
      \begin{equation}
        \label{conv:proof:normalregen}
        \ceil*{\frac{a + b}{\regen}} \geq 2 \Rightarrow \frac{a + b}{\regen} >
        1 \Rightarrow a + b > \regen\enspace.
      \end{equation}
      Thus $\forall \pid \in \left[\playerlen\right], \votpowvecreg_{\pid, r_2}
      = 1 - a - b + \regen \overset{(\ref{conv:proof:normalregen})}{<} 0$, thus
      $i = 2$.
    \end{itemize}
    We proved that $i$ exists. Since all players follow the same voting pattern,
    the voting power of all players in each round is the same. Let $\rvp =
    \votpowvecreg_{1, \round_i}$. Assume that $\attspan < i \vee i > 2$. We
    cover the case where $\attspan \geq i \wedge i = 2$ later. In case
    $\playerlen$ is even, let $0 < \gamma < 0, 0 < \epsilon < \gamma\left(1 -
    \rvp\right)$,

    \begin{gather*}
      \weakpost = \left(\underbrace{1, \dots, 1}_{\playerlen/2},
      \underbrace{\gamma - \epsilon, \dots, \gamma -
      \epsilon}_{\playerlen/2}\right) \enspace, \\
      \strongpost = \left(\underbrace{\gamma, \dots, \gamma}_{\playerlen/2},
      \underbrace{1, \dots, 1}_{\playerlen/2}\right) \enspace, \\
      \nullpost = \left(\underbrace{0, \dots, 0}_{\playerlen}\right) \enspace,
      \\
      \postlist = \left[\underbrace{\weakpost, \dots, \weakpost}_{i - 1},
      \strongpost, \underbrace{\nullpost, \dots, \nullpost}_{\postlen -
      i}\right] \enspace.
    \end{gather*}

    First of all, it is
    \begin{gather*}
      \forall j \in \left[i - 1\right], \idsc{\postlist\left[j\right]} =
      \frac{\playerlen}{2}\left(1 + \gamma - \epsilon\right) < \\
      < \frac{\playerlen}{2}\left(1 + \gamma\right) =
      \idsc{\postlist\left[i\right]}
    \end{gather*}
    and $\forall j \in \left\{i + 1, \dots,
    \postlen\right\}, \idsc{\postlist\left[j\right]} = 0 <
    \idsc{\postlist\left[i\right]}$, thus the strong post has strictly the
    highest ideal score of all posts and as a result, $\forall \postlist'$ that
    contains the same posts as $\postlist$ and
    $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[i\right]$.

    We observe that all players like both weak and strong posts more than null
    posts, thus no player will vote for a null post unless her attention span
    contains only null posts. This can happen in two cases: First, if the player
    has not yet voted for all non-null posts, but the first $\attspan$ posts of
    the list, excluding already voted posts, are null posts. Second, if the
    player has already voted for all non-null posts. For a null post to rank
    higher than a non-null one, it must be true that there exists one player
    that has cast the first vote for the null post. However, since the null
    posts are initially at the bottom of the list and it is impossible for a
    post to improve its ranking before it is voted, we deduce that this first
    vote can be cast only after the voter has voted for all non-null posts. We
    deduce that all players vote for all non-null posts before voting for any
    null post.

    We will now see that the first $\frac{\playerlen}{2}$ players vote first for
    all weak posts and then for the strong post. These players like the weak
    posts more than the strong post. As we saw, they will not vote any null
    post before voting for all non-null ones. If $\attspan > 1$ they vote for
    the strong post only when all other posts in their attention span are null
    ones and thus they will have voted for all weak posts already. If $\attspan
    = 1$ and since no post can increase its position before being voted, the
    strong post will become ``visible'' for all players only once they have
    voted for all weak posts. Thus in both cases the first
    $\frac{\playerlen}{2}$ players vote for the strong post only after they have
    voted for all weak posts first.

    The two previous results combined prove that the first
    $\frac{\playerlen}{2}$ players vote for the strong post in round $\round_i$
    exactly. We also observe that these players have experienced the exact same
    voting power reduction and regeneration as in the case of $\postlist^1$
    since they voted only for posts with likeability 1, thus in round $\round_i$
    their voting power after regeneration is exactly the same as in the case of
    $\postlist^1: \forall \pid \in
    \left[\frac{\playerlen}{2}\right], \votpowvecreg_{\pid, \round_i} =
    \rvp$.

    We observe that the first $\frac{\playerlen}{2}$ players vote for all weak
    posts with full voting power. As for the last $\frac{\playerlen}{2}$
    players, we observe that, if $\attspan < i$, they all vote for the first
    weak post of the list in the first round, and thus with full voting power. If
    $\attspan \geq i$ and $i > 2$, they vote for the strong post in the first
    round and for the first weak post in $r_2$ with full voting power. Thus in
    all cases the last $\frac{\playerlen}{2}$ players vote for the first weak
    post with full voting power. Therefore, the score of the first weak post at
    the end of the execution is
    $\mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) =
    \frac{\playerlen}{2}\left(a + b\right) +
    \frac{\playerlen}{2}\left(\left(\gamma - \epsilon\right) a + b\right)$.

    On the other hand, at the end of the execution the strong post has been
    voted by the first $\frac{\playerlen}{2}$ players with $\rvp$
    voting power and by the last $\frac{\playerlen}{2}$ players with at most
    full voting power, thus its final score will be at most
    $\mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) \leq
    \frac{\playerlen}{2}\left(\rvp \cdot \gamma a + b\right) +
    \frac{\playerlen}{2}\left(a + b\right)$. It is
    \begin{gather*}
      \epsilon < \gamma\left(1 - \rvp\right) \Rightarrow \\
      \frac{\playerlen}{2}\left(\rvp \cdot \gamma a + b\right) +
      \frac{\playerlen}{2}\left(a + b\right) < \frac{\playerlen}{2}\left(a +
      b\right) + \frac{\playerlen}{2}\left(\left(\gamma - \epsilon\right) a +
      b\right) \Rightarrow \\
      \mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) <
      \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) \enspace.
    \end{gather*}

    Thus $\postlist_{\rounds}\left[1\right] \neq \postlist\left[i\right]$ and
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.

    As for the case when $\playerlen$ is odd, let $0 < \epsilon <
    \gamma\frac{\playerlen - 3}{\playerlen - 1}\left(1 - \rvp\right)$.
    In this case, we assume that the likeability of the first $i$ posts (weak
    and strong) for the last player is $\gamma$, whereas the likeability of
    the last $\postlen - i$ posts (the null posts) is 0. This means that the
    last player votes first for the weak and strong posts and then for the
    null posts. The rest of the likabilities remain as in the case when
    $\playerlen$ is even. We observe that the ideal score of the strong post
    is still strictly higher than the rest. Furthermore, since the last player
    votes for the first weak post within the first $i$ voting rounds, her
    voting power at the time of this vote will be at least $\rvp$. We thus
    have the following bounds for the scores:

    \begin{gather*}
      \mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) \leq
      \frac{\playerlen - 1}{2}\left(\rvp \cdot \gamma a + b\right) +
      \frac{\playerlen - 1}{2}\left(a + b\right) + \gamma a + b \enspace, \\
      \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) \geq
      \frac{\playerlen - 1}{2}\left(a + b\right) + \frac{\playerlen -
      1}{2}\left(\left(\gamma - \epsilon\right) a + b\right) + \rvp \cdot \gamma
      a + b \enspace.
    \end{gather*}

    Given the bounds of $\epsilon$, it is
    $\mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) <
    \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right)$, thus
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.

    We finally cover the previously untreated edge case where $\attspan \geq i
    \wedge i = 2$. $\rvp$ is defined like before. We first consider the case
    when $\playerlen$ is even and greater than 2: $\exists k \in \mathbb{N}
    \setminus \left\{0, 1\right\}: \playerlen = 2k$. Let $0 < \gamma < 1, 0 <
    \epsilon < 2 \gamma \frac{1 - \rvp}{\left(k - 1\right)\rvp}$,
    \begin{gather*}
      \weakpost = \left(\underbrace{1, \dots, 1}_{k - 1}, \underbrace{\gamma -
      \epsilon, \dots, \gamma - \epsilon}_{k - 1}, \gamma, \gamma\right)
      \enspace, \\
      \strongpost = \left(\underbrace{\gamma, \dots, \gamma}_{k - 1},
      \underbrace{1, \dots, 1}_{k - 1}, \gamma, \gamma\right) \enspace, \\
      \postlist = \left[\weakpost, \strongpost, \underbrace{\nullpost, \dots,
      \nullpost}_{\postlen - 2}\right] \enspace.
    \end{gather*}
    We first observe that
    \begin{gather*}
      \forall j \in \left\{3, \dots, \postlen\right\},
      \idsc{\postlist\left[j\right]} = 0 < \\
      < \idsc{\postlist\left[1\right]} = k - 1 + \left(k - 1\right)\left(\gamma
      - \epsilon\right) + 2\gamma = \\
      = k - 1 + \left(k + 1\right)\gamma - \left(k - 1\right)\epsilon < \\
      < k - 1 + \left(k + 1\right)\gamma = \idsc{\postlist\left[2\right]}
      \enspace,
    \end{gather*}
    thus the strong post has strictly the highest ideal score of all posts and
    as a result, $\forall \postlist'$ that contains the same posts as
    $\postlist$ and $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[2\right]$.

    The first $k - 1$ and the last two players vote first for
    $\postlist\left[1\right]$ and then for $\postlist\left[2\right]$, whereas
    players $k, \dots, 2k - 2$ vote first for $\postlist\left[2\right]$ and then
    for $\postlist\left[1\right]$, thus at the end of the execution,
    \begin{gather*}
      \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) = \left(k -
      1\right)\left(a + b\right) + 2\left(\gamma a + b\right) + \left(k -
      1\right)\left(\left(\gamma - \epsilon\right)\rvp a + b\right) \enspace, \\
      \mathrm{sc}_{\rounds}\left(\postlist\left[2\right]\right) = \left(k -
      1\right)\left(a + b\right) + \left(k + 1\right)\left(\gamma \rvp a +
      b\right) \enspace.
    \end{gather*}
    Given the bound on $\epsilon$, it is
    $\mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) >
    \mathrm{sc}_{\rounds}\left(\postlist\left[2\right]\right)$, thus
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.

    Second, we consider the case when $\playerlen$ is odd: $\exists k \in
    \mathbb{N}: \playerlen = 2k + 1$. Let $0 < \gamma < 1, 0 <
    \epsilon < \gamma \frac{1 - \rvp}{k\rvp}$,
    \begin{gather*}
      \weakpost = \left(\underbrace{1, \dots, 1}_{k}, \underbrace{\gamma -
      \epsilon, \dots, \gamma - \epsilon}_{k}, \gamma\right) \enspace, \\
      \strongpost = \left(\underbrace{\gamma, \dots, \gamma}_{k}, \underbrace{1,
      \dots, 1}_{k}, \gamma\right) \enspace, \\
      \postlist = \left[\weakpost, \strongpost, \underbrace{\nullpost, \dots,
      \nullpost}_{\postlen - 2}\right] \enspace.
    \end{gather*}
    We first observe that
    \begin{gather*}
      \forall j \in \left\{3, \dots, \postlen\right\},
      \idsc{\postlist\left[j\right]} = 0 < \\
      < \idsc{\postlist\left[1\right]} = k + k\left(\gamma - \epsilon\right) +
      \gamma = \\
      = k + \left(k + 1\right)\gamma -k\epsilon < k + \left(k + 1\right)\gamma =
      \idsc{\postlist\left[2\right]} \enspace,
    \end{gather*}
    thus the strong post has strictly the highest ideal score of all posts and
    as a result, $\forall \postlist'$ that contains the same posts as
    $\postlist$ and $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[2\right]$.

    The first $k$ and the last player vote first for $\postlist\left[1\right]$
    and then for $\postlist\left[2\right]$, whereas players $k + 1, \dots, 2k$
    vote first for $\postlist\left[2\right]$ and then for
    $\postlist\left[1\right]$, thus at the end of the execution,
    \begin{gather*}
      \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) = k\left(a +
      b\right) + \gamma a + b + k\left(\left(\gamma - \epsilon\right)\rvp a +
      b\right) \enspace, \\
      \mathrm{sc}_{\rounds}\left(\postlist\left[2\right]\right) = k\left(a +
      b\right) + \left(k + 1\right)\left(\gamma \rvp a + b\right) \enspace.
    \end{gather*}
    Given the bound on $\epsilon$, it is
    $\mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) >
    \mathrm{sc}_{\rounds}\left(\postlist\left[2\right]\right)$, thus
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.

    Last but not least, we consider the case when $\playerlen = 2$. In this
    case, let $0 < \gamma < 1$ and
    \begin{equation*}
      \postlist = \left[\left(1, 0\right), \left(\gamma, 1 - \gamma\frac{1 +
      \rvp}{2}\right), \underbrace{\nullpost, \dots, \nullpost}_{\postlen -
      2}\right] \enspace.
    \end{equation*}
    It is $\forall j \in \left\{3, \dots, \postlen\right\},
    \idsc{\postlist\left[j\right]} = 0 < \idsc{\postlist\left[1\right]} = 1
    \overset{\rvp < 1}{<} 1 + \gamma\frac{1 - \rvp}{2} = \gamma + 1 -
    \gamma\frac{1 +\rvp}{2} = \idsc{\postlist\left[2\right]}$, thus
    $\postlist\left[2\right]$ has strictly the highest ideal score of all posts
    and as a result, $\forall \postlist'$ that contains the same posts as
    $\postlist$ and $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[2\right]$.

    On the other hand,
    $\mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) = a + 2b > \gamma
    \rvp a + b + \left(1 - \gamma \frac{1 + \rvp}{2}\right) a + b =
    \mathrm{sc}_{\rounds}\left(\postlist\left[2\right]\right)$, thus
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.
  \end{itemize}
\end{proof}
