\section{Further Work}

  We have studied the curation properties of decentralized content curation
  platforms such as Steemit, obtaining new insights on the resilience of these
  systems. Some assumptions have been made in the presented model. Various
  relaxations of these assumptions constitute fertile ground for future work.
  First of all, the selfish strategy can be extended and refined in various
  ways. For example, in a more general case voting rings can have the ability to
  create more than one posts in order to increase their rewards. Optimizing the
  number of posts and the vote allocation in this case would contribute towards
  a robust attack against the Steemit platform.

  Selfish behavior is considered only in the simulation. Our theoretic results
  can be complemented with an analysis of games with selfish players.

  Another open problem is the role of wealth distribution among players. In
  Steemit, the influence of the votes is weighed by the amount of coins each
  user has staked in the platform, a number known as Steem Power~\cite{steemit}.
  We have chosen to omit this concept, which effectively mitigates the
  possibility of Sybil attacks but increases the influence of wealthy
  individuals to the curation procedure. Including the distribution of wealth in
  our model may provide more realistic results and capture the relative
  influence of big stakeholders.

  The addition of the economic factor invites the definition of utility
  functions and strategic behavior for the players. Its inclusion would imply
  the need for an expansion of our theorems and definitions to the strategic
  case, along with a full game-theoretic analysis. Furthermore, several possible
  refinements could be introduced; for example, the process of creating Sybil
  accounts could be associated with a monetary cost.

  Last but not least, in our model posts are created only at the beginning of
  the execution. An extended model in which authors can create posts at any time
  and where the execution continues indefinitely (as is the case in real-world
  content curation systems) will provide further intuition on the topic of
  decentralized curation.
