\section{Introduction}
  The modern Internet contains an immense amount of data; a single user can only consume a tiny fraction in a reasonable amount of time. Therefore, any widely used platform that hosts user-generated content (UGC) must employ a content curation mechanism.
   Content curation can be understood as the set of mechanisms which rank, aggregate and filter relevant information. In recent years, popular news aggregation sites like Reddit\footnote{\url{https://www.reddit.com/} Accessed: 2018-09-25} or Hacker News\footnote{\url{https://news.ycombinator.com/} Accessed: 2018-09-25} have established crowdsourced curation as the primary way to filter content for their users.
   Crowdsourced content curation, as opposed to more traditional techniques such as expert- or algorithmic-based curation, orders and filters content based on the ratings and feedback of the users themselves, obviating the need for a central moderator by leveraging the ``wisdom of the crowd''~\cite{askalidis2013theoretical}.

  The decentralized nature of crowdsourced curation makes it a suitable solution for ranking user-generated content in blockchain-based content hosting systems. The aggregation and filtering of user-generated content emerges as a particularly challenging problem in permissionless blockchains, as any solution that requires a concrete moderator implies that there exists a privileged party, which is incompatible with a permissionless blockchain.
   Moreover, public blockchains are easy targets for Sybil attacks, as any user can create new accounts at any time for a marginal cost.
    Therefore, on-chain mechanisms to resist the effect of Sybil users are necessary for a healthy and well-functioning platform; traditional counter-Sybil mechanisms~\cite{levine2006survey} are much harder to apply in the case of blockchains due to the decentralized nature of the latter.
   The functions performed by moderators in traditional content platforms need to be replaced by incentive mechanisms that ensure self-regulation. Having the impact of a vote depend on the number of coins the voter holds is an intuitively appealing strategy to achieve a proper alignment of incentives for users in decentralized content platforms; specifically, it can render Sybil attacks impossible.

   However, the correct design of such systems is still an unsolved problem. Blockchains have created a new economic paradigm where users are at the same time equity holders in the system, and leveraging this property in a robust manner constitutes an interesting challenge.
   A variety of projects have designed decentralized content curation systems~\cite{synereo,steemit,tcr}. Nevertheless, a deep understanding of the properties of such systems is still lacking. Among them, Steemit
has a long track record, having been in operation since 2016 and attaining a user base of more than 1.08 M\footnote{\url{https://steemdb.com/accounts} Accessed: 2018-09-25} registered accounts\footnote{The number of accounts should not be understood as the number of active users, as one user can create multiple accounts.}. Steemit is a social media platform which lets users earn money (in the form of the STEEM cryptocurrency) by both creating and curating content in the network. Steemit is the front-end of the social network, a graphical web interface which allows users to see the content of the platform. On the other hand, all the back-end information is stored on a distributed ledger, the Steem blockchain. Steem can be understood as an ``app-chain'', a blockchain with a specific application purpose: serving as a distributed database for social media applications~\cite{steemit}.

\noindent  \textbf{Our Contributions.}
In this work we study the foundations of decentralized content curation from a computational perspective. We develop an abstract model of a post-voting system which aims to sort the posts created by users in a distributed and crowdsourced manner.
  Our model is constituted by a functionality which executes a protocol performed by $N$ players. The model includes an honest participant behaviour while it allows deviations to be modeled for a subset of the participants.      The $N$ players contribute votes in a round-based curation process. The impact of each vote depends on the number of coins held by the player.
   The posts are arranged in a list, sorted by the value of votes received, resembling the front-page model of Reddit or Hacker News. In the model, players vote according to their subjective opinion on the quality of the posts and have a limited attention span.

   Following previous related work~\cite{ghosh2011incentivizing,askalidis2013theoretical}, we represent each player's opinion on each post (i.e. likability) with a numerical value $\like \in [ 0,1 ]$.
   The objective quality of a post is calculated as the simple summation of all players' likabilities for the post in question. 
   To measure the effectiveness of a post-voting system, we introduce the property of  \textit{convergence} under honesty which is parameterised by a number of values including a metric $t$, that demands the  first $t$ articles to be   ordered according to the objective quality of the posts at the end of the execution assuming all participants signal honestly to the system their personal preferences. 
Armed with our  post-voting system abstraction, we proceed to particularize it to model Steemit and provide the following results. 


\begin{itemize}
\item[i] We characterise the conditions under which our abstract Steemit model converges highlighting the number of rounds that the system requires in order to converge under honesty for any sequence of posts. 
\item[ii]
We validate our results with a simulation testing different metrics based on  correlation that have been proposed in previous work and relating them to our notion of convergence. 
\item[iii]
We demonstrate that ``selfish''  deviation from honest behavior results to substantial gains in terms of boosting the ranking of specific posts  in the resulting list of the post-voting system. 
\end{itemize}
%   Our analysis of the post-voting system of Steemit aims to provide a useful framework to aid the design of future decentralized curation platforms. 

%  \begin{itemize}
%  \item Original treatment following cryptography and simulation-based techniques to model crowdsourced content curation, in opposition to previous academic work which have leaned more towards an analytical and game-theoretic approach.

%  \item Taking in account of subjective likeabilities, the effect of rounds and an agnostic likeability distribution treatment.

%  \item Measurement of the influence of coin-holding (wealth-distribution) in the effectivity of post sorting. New paradigm present in blockchain based systems (main difference with Reddit-like platforms.)

 % \item Proof that Steem does not t-converge with the parameters currently used in their implementation. Insights to improve the curation quality of the trending section of steem.

 % \item (Maybe)Impact of the curation quality when greedy players are present in the system.
 % \end{itemize}
