\begin{proof}
  \begin{itemize}
    \item ($\Leftarrow$) Suppose that
    \begin{gather}
      \label{conv:proof:rev}
      \rounds - 1 \geq \left(\postlen - 1\right)\ceil*{\frac{a+b}{\regen}} \\
      \text{and } \forall i \in \left[\playerlen\right], \stpowvec_i = c
      \enspace. \nonumber
    \end{gather}
    Let $\pid \in \left[\playerlen\right]$. In this case it is $\rounds \geq
    \postlen$ and according to \textsc{VoteThisRound} in
    Algorithm~\ref{alg:steem:vote}, $u_{\pid}$ votes non-null in rounds
    $\left(\round_1, \dots, \round_\postlen\right)$ with $r_i = \floor*{\left(i
    - 1\right)\frac{\rounds - 1}{\postlen - 1}} + 1$. Observe that:
    \begin{gather}
      \label{conv:proof:integer}
      \left(\ref{conv:proof:rev}\right) \Rightarrow \frac{\rounds - 1}{\postlen
      - 1} \geq \ceil*{\frac{a+b}{\regen}}
      \underset{\text{integer}}{\overset{\text{rhs}}{\Rightarrow}}
      \floor*{\frac{\rounds - 1}{\postlen - 1}} \geq \ceil*{\frac{a+b}{\regen}}
      \enspace, \\
      \label{conv:proof:step}
      \forall i \in \left[\postlen\right] \setminus \left\{1\right\}, r_i
      \in \left\{r_{i - 1} + \floor*{\frac{\rounds - 1}{\postlen - 1}}, r_{i -
      1} + \ceil*{\frac{\rounds - 1}{\postlen - 1}}\right\} \enspace.
    \end{gather}
    From (\ref{conv:proof:integer}) and (\ref{conv:proof:step}) we have that
    $\forall i \in \left[\postlen - 1\right], r_{i+1} - r_i \geq
    \ceil*{\frac{a+b}{\regen}}$. We will now prove by induction that $\forall i
    \in \left[\postlen\right], \votpowvec_{\pid, r_i} = 1$.

    \begin{itemize}
      \item For $i = 1, \votpowvec_{\pid, 1} = 1$ by
      (Algorithm~\ref{alg:steem:init}, line~\ref{alg:steem:init:vp}).  \item Let
      $\votpowvec_{\pid, r_i} = 1$. Until $r_{i + 1}$, a single non-null vote is
      cast by $u_\pid$, which reduces $\votpowvec_{\pid}$ by at most $a + b$
      (Algorithm~\ref{alg:steem:handlevote},
      line~\ref{alg:steem:handlevote:cost:start}) and at least $\ceil*{\frac{a +
      b}{\regen}}$ regenerations, each of which replenishes $\votpowvec_{\pid}$
      by $\regen$. Thus
      \begin{equation*}
        \votpowvec_{\pid, r_{i + 1}} \geq \min{\left\{\votpowvec_{\pid, r_i} - a
        - b + \regen\ceil*{\frac{a + b}{\regen}}, 1\right\}} \geq 1 \enspace.
      \end{equation*}
      But $\votpowvec_{\pid}$ cannot exceed 1
      (line~\ref{alg:steem:handlevote:regen}), thus $\votpowvec_{\pid, r_{i +
      1}} = 1$.
    \end{itemize}
    Since the above holds for every $\pid \in \left[\playerlen\right]$, we have
    that at the end of the execution, all votes have been cast with full voting
    power, thus $\forall \post = \left(i, \like\right) \in \postlist_\rounds,
    \mathrm{scores}_{p} = c\left(\playerlen b + a \sum\limits_{\pid =
    1}^\playerlen \like_{\pid}\right)$ and the posts in $\postlist_R$ are sorted
    by decreasing score (Algorithm~\ref{alg:steem:handlevote},
    line~\ref{alg:steem:handlevote:order}). We observe that
    \begin{gather*}
      \forall p_1 = \left(j^1, \like^1\right) \neq p_2 = \left(j^2,
      \like^2\right) \in \postlist_R, \idsc{p_1} > \idsc{p_2} \Rightarrow \\
      \sum\limits_{i = 1}^\playerlen \like^1_i > \sum\limits_{i = 1}^\playerlen
      \like^2_i \Rightarrow c\left(\playerlen b + a \sum\limits_{i =
      1}^\playerlen \like^1_i\right) > c\left(\playerlen b + a \sum\limits_{i =
      1}^\playerlen \like^2_i\right) \enspace.
    \end{gather*}
    Thus all posts will be ordered according to their ideal scores; put
    otherwise, $\textsc{IdealScore}^M\left(\postlist_\rounds\right)$ holds.

    \item ($\stpowvec$ variable $\Rightarrow$ no convergence) Let $\postlist =
    \left(\left(1, \left(a_1, \dots, a_\playerlen\right)\right), \left(2,
    \left(b_1, \dots, b_\playerlen\right)\right)\right)$ such that the following
    linear constraints are simultaneously feasible:
    \begin{gather*}
      \sum\limits_{i=1}^\playerlen a_i > \sum\limits_{i=1}^\playerlen b_i \\
      \sum\limits_{i=1}^\playerlen \stpow_i a_i < \sum\limits_{i=1}^\playerlen
      \stpow_i  b_i
    \end{gather*}
    I think that's always possible if $\stpow$ is not constant.

    \item (inequality doesn't hold $\Rightarrow$ no convergence) Suppose that
    \begin{gather}
      \label{conv:proof:fewrounds}
      \rounds - 1 < \left(\postlen - 1\right)\ceil*{\frac{a+b}{\regen}} \\
      \text{and } \forall i \in \left[\playerlen\right], \stpowvec_i = c
      \enspace. \nonumber
    \end{gather}
    If $\rounds < \postlen$ things are easier TODO: prove this.

    Assume $\rounds \geq \postlen$. In this case, all posts receive a vote by
    all players. Consider $\postlist^1 = 1^{\postlen \times \playerlen}$ and
    $\pid \in \left[\playerlen\right]$. Let
    \begin{equation*}
      i \in \left[\postlen\right] :\left(\votpowvecreg_{\pid, \round_i} < 1
      \wedge \nexists i' < i: \votpowvecreg_{\pid, \round_{i'}} < 1\right)
      \enspace,
    \end{equation*}
    i.e. $i$ is the first round in which $u_\pid$ votes with less than full
    voting power. Since the first round is a voting round and the voting power
    of all players is full, it is $i \geq 2$. (Such a round exists because of
    eq.~(\ref{conv:proof:fewrounds}). TODO: prove this) Since all players follow
    the same voting pattern, the voting power of all players in each round is
    the same. Let $\mathrm{reducedVP} = \votpowvecreg_{1, \round_i}$. For now
    assume $2 | N$ and $\attspan < i \vee i > 2$. Let $0 < \gamma < 1$ and $0 <
    \epsilon < \gamma\left(1 - \mathrm{reducedVP}\right)$.
    \begin{gather*}
      \mathrm{weakPost} = \left(1, \left(\underbrace{1, \dots,
      1}_{\playerlen/2}, \underbrace{\gamma - \epsilon, \dots, \gamma -
      \epsilon}_{\playerlen/2}\right)\right) \enspace, \\
      \mathrm{strongPost} = \left(1, \left(\underbrace{\gamma, \dots,
      \gamma}_{\playerlen/2}, \underbrace{1, \dots,
      1}_{\playerlen/2}\right)\right) \enspace, \\
      \mathrm{nullPost} = \left(1, \left(\underbrace{0, \dots,
      0}_{\playerlen}\right)\right) \enspace, \\
      \postlist = \left[\underbrace{\mathrm{weakPost}, \dots,
      \mathrm{weakPost}}_{i - 1}, \mathrm{strongPost},
      \underbrace{\mathrm{nullPost}, \dots, \mathrm{nullPost}}_{\postlen -
      i}\right] \enspace.
    \end{gather*}

    First of all, it is $\forall j \in \left[i - 1\right],
    \idsc{\postlist\left[j\right]} = \frac{\playerlen}{2}\left(1 + \gamma -
    \epsilon\right) < \frac{\playerlen}{2}\left(1 + \gamma\right) =
    \idsc{\postlist\left[i\right]}$ and $\forall j \in \left\{i + 1, \dots,
    \postlen\right\}, \idsc{\postlist\left[j\right]} = 0 <
    \idsc{\postlist\left[i\right]}$, thus the strong post has strictly the
    highest ideal score of all posts and as a result, $\forall \postlist'$ that
    contains the same posts as $\postlist$ and
    $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[i\right]$.

    We observe that all players like both weak and strong posts more than null
    posts, thus no player will vote for a null post unless her attention span
    contains only null posts. This can happen in two cases: First, if the player
    has not yet voted for all non-null posts, but the first $\attspan$ posts of
    the list, excluding already voted posts, are null posts. Second, if the
    player has already voted for all non-null posts. For a null post to rank
    higher than a non-null one, it must be true that there exists one player
    that has cast the first vote for the null post. However, since the null
    posts are initially at the bottom of the list and it is impossible for a
    post to improve its ranking before it is voted, we deduce that this first
    vote can be cast only after the voter has voted for all non-null posts. We
    deduce that all players vote for all non-null posts before voting for any
    null post.

    We will now see that the first $\frac{\playerlen}{2}$ players vote first for
    all weak posts and then for the strong post. These players like the weak
    posts more than the strong post. As we saw, they will not vote any null
    post before voting for all non-null ones. If $\attspan > 1$ they vote for
    the strong post only when all other posts in their attention span are null
    ones and thus they will have voted for all weak posts already. If $\attspan
    = 1$ and since no post can increase its position before being voted, the
    strong post will become ``visible'' for all players only once they have
    voted for all weak posts. Thus in both cases the first
    $\frac{\playerlen}{2}$ players vote for the strong post only after they have
    voted for all weak posts first.

    The two previous results combined prove that the first
    $\frac{\playerlen}{2}$ players vote for the strong post in round $\round_i$
    exactly. We also observe that these players have experienced the exact same
    voting power reduction and regeneration as in the case of $\postlist^1$
    since they voted only for posts with likeability 1, thus in round $\round_i$
    their voting power after regeneration is exactly the same as in the case of
    $\postlist^1: \forall \pid \in
    \left[\frac{\playerlen}{2}\right], \votpowvecreg_{\pid, \round_i} =
    \mathrm{reducedVP}$.

    We observe that the first $\frac{\playerlen}{2}$ players vote for all weak
    posts with full voting power. As for the last $\frac{\playerlen}{2}$
    players, we observe that, if $\attspan < i$, they all vote for the first
    weak post of the list in the first round, and thus with full voting power. If
    $\attspan \geq i$ and $i > 2$, they vote for the strong post in the first
    round and for the first weak post in $r_2$ with full voting power. Thus in
    all cases the last $\frac{\playerlen}{2}$ players vote for the first weak
    post with full voting power. Therefore, the score of the first weak post at
    the end of the execution is
    $\mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) =
    c\left(\frac{\playerlen}{2}\left(a + b\right) +
    \frac{\playerlen}{2}\left(\left(\gamma - \epsilon\right) a +
    b\right)\right)$.

    On the other hand, at the end of the execution the strong post has been
    voted by the first $\frac{\playerlen}{2}$ players with $\mathrm{reducedVP}$
    voting power and by the last $\frac{\playerlen}{2}$ players with at most
    full voting power, thus its final score will be at most
    $\mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) \leq
    c\left(\frac{\playerlen}{2}\left(\mathrm{reducedVP} \cdot \gamma a +
    b\right) + \frac{\playerlen}{2}\left(a + b\right)\right)$. It is
    \begin{gather*}
      \epsilon < \gamma\left(1 - \mathrm{reducedVP}\right) \Rightarrow \\
      c\left(\frac{\playerlen}{2}\left(a + b\right) +
      \frac{\playerlen}{2}\left(\left(\gamma - \epsilon\right) a +
      b\right)\right) < c\left(\frac{\playerlen}{2}\left(\mathrm{reducedVP}
      \cdot \gamma a + \frac{\playerlen}{2}\left(a + b\right)\right)\right)
      \Rightarrow \\
      \mathrm{sc}_{\rounds}\left(\postlist\left[i\right]\right) <
      \mathrm{sc}_{\rounds}\left(\postlist\left[1\right]\right) \enspace.
    \end{gather*}

    Thus $\postlist_{\rounds}\left[1\right] \neq \postlist\left[i\right]$ and
    $\mathrm{Ideal}^1\left(\postlist_{\rounds}\right)$ does not hold.

    ----------------------- Attempt 2

    Let $\postlist = \left[\left(1, \underbrace{\left(1, 0.5 + \epsilon, 0,
    \dots, 0\right)}_{\playerlen}\right), \left(1, \underbrace{\left(0, 0.5, 0,
    \dots, 0\right)}_{\playerlen}\right), \left(1, \underbrace{\left(0, \dots,
    0\right)}_{\playerlen}\right), \dots, \left(1, \underbrace{\left(0, \dots,
    0\right)}_{\playerlen}\right)\right]$. Observe that
    $\idsc{\postlist\left[1\right]} = 1, \idsc{\postlist\left[2\right]} = 1 +
    \epsilon$ and $\forall i \in \left[\postlen\right] \setminus \left\{1,
    2\right\}, \idsc{\postlist\left[i\right]} = 0$, thus $\forall \postlist'$
    that contains the same posts as $\postlist$ and
    $\textsc{Ideal}^1\left(\postlist'\right)$ holds, it is
    $\postlist'\left[1\right] = \postlist\left[2\right]$.

    \begin{itemize}
      \item $\rounds = 1, \attspan = 1$ \\
      In the first round, $u_1$ casts a vote of weight 1 and the rest of the
      players cast a vote of weight 0 for $\postlist\left[1\right]$, thus at the
      end of the execution, $\mathrm{scores}_1 = c \left(a + b\right) +
      \left(\playerlen - 1\right) c b$. No other votes are cast, thus
      $\mathrm{scores}_2 = 0$. Thus at the end of the execution
      $\mathrm{scores}_1 > \mathrm{scores}_2$.

      \item $\rounds = 1, \attspan > 1$ \\
      In the first round, $u_1$ casts a vote of weight 1 for
      $\postlist\left[1\right]$, $u_2$ casts a vote of weight 0.5 for
      $\postlist\left[2\right]$ and all other players cast a vote of weight 0
      for $\postlist\left[1\right]$. No other votes are cast. Thus at the end of
      the execution, $\mathrm{scores}_1 = c\left(a + b\right) + \left(\playerlen
      - 2\right) c b$ and $\mathrm{scores}_2 = c\left(0.5a + b\right)$. We
      deduce that $\mathrm{scores}_1 > \mathrm{scores}_2$.

      \item $\rounds > 1, \attspan = 1$ \\
      In the first round, the votes are identical to the previous case. As we
      saw in eq.~(\ref{conv:proof:step}), the next vote will be cast not earlier
      than round $\ceil*{\frac{\rounds - 1}{\postlen - 1}}$ and not later than
      round $\ceil*{\frac{\rounds - 1}{\postlen - 1}} + 1$, thus
      $\ceil*{\frac{\rounds - 1}{\postlen - 1}} \leq \round_2 \leq
      \ceil*{\frac{\rounds - 1}{\postlen - 1}} + 1 \Rightarrow \votpowvecreg_{1,
      \round_2} \leq \min{\left\{1 - a - b + \regen\ceil*{\frac{\rounds -
      1}{\postlen - 1}}, 1\right\}}$

      \item $\rounds > 1, \attspan > 1$ \\
    \end{itemize}
    In every case, $\postlist_\rounds$ is ordered in descending post score
    (Algorithm~\ref{alg:steem:handlevote},
    line~\ref{alg:steem:handlevote:order}), thus
    $\postlist_\rounds\left[1\right] \neq \postlist\left[2\right]$ and the
    property $\mathrm{Ideal}^1\left(\postlist_\rounds\right)$ does not hold.

    ----------------------------- Attempt 1

    \begin{itemize}
      \item $\rounds < \postlen \wedge \attspan < \postlen$ \\
      At the end of the execution all players will have voted for
      $\postlist\left[1\right]$ in the first round, and thus
      $\mathrm{scores}_{\postlist\left[1\right]} = \playerlen c \left(0.5a +
      b\right)$. On the other hand, $\postlist\left[\postlen\right]$ will have
      been voted by at most $u_\playerlen$ with voting power $\votpow \leq 1 -
      \left(0.5a + b\right) + \regen$, thus \\
      $\mathrm{scores}_{\postlist\left[\postlen\right]} \leq c \left(\left(1 -
      \left(0.5a + b\right) + \regen\right)\left(0.5 + \epsilon\right)a +
      b\right) \overset{\regen < b}{<} c\left(\left(0.5 + \epsilon\right)a +
      b\right)$. Thus $\mathrm{scores}_{\postlist\left[1\right]} >
      \mathrm{scores}_{\postlist\left[\postlen\right]} \Leftrightarrow \left(N
      - 1\right)\left(0.5 + \frac{b}{a}\right) > \epsilon$. TODO: choose
      $\epsilon$ and show non-convergence

      \item $\rounds < \postlen \wedge \attspan = \postlen$ \\
      At the end of the execution, all players except for $u_\playerlen$ will
      have voted for $\postlist\left[1\right]$ in the first round, and thus
      $\mathrm{scores}_{\postlist\left[1\right]} \geq \left(\playerlen -
      1\right) c \left(0.5a + b\right)$. On the other hand,
      $\postlist\left[\postlen\right]$ will have been voted by exactly
      $u_\playerlen$ and this vote will have been cast on the first round, thus
      $\mathrm{scores}_{\postlist\left[\postlen\right]} = c\left(\left(0.5 +
      \epsilon\right)a + b\right)$. Thus
      $\mathrm{scores}_{\postlist\left[1\right]} >
      \mathrm{scores}_{\postlist\left[\postlen\right]} \Leftrightarrow \left(N
      - 2\right)\left(0.5 + \frac{b}{a}\right) > \epsilon$. TODO: choose
      $\epsilon$ and show non-convergence

      \item $\rounds \geq \postlen \wedge \attspan < \postlen$ \\
      In this case, all players vote for all posts.  At the end of the execution
      all players will have voted for $\postlist\left[1\right]$ in the first
      round, and thus $\mathrm{scores}_{\postlist\left[1\right]} = \playerlen c
      \left(0.5a + b\right)$. As far as $\postlist\left[\postlen\right]$ is
      concerned, we first observe that the distance between to voting rounds is
      $\ceil*{\frac{\rounds - 1}{\postlen - 1}}$ at most: $\forall i \in
      \left[M - 1\right], r_{i+1} - r_i \leq \ceil*{\frac{\rounds - 1}{\postlen
      - 1}}$. Thus the voting power of all players will be at most
      $\regen\floor*{\frac{\rounds - 1}{\postlen - 1}}$ before voting for the
      last post. We deduce that
      $\mathrm{scores}_{\postlist\left[\postlen\right]}$
      
      will have
      been voted by all players except for $u_{\playerlen}$ with voting power at
      most

      \item $\rounds \geq \postlen \wedge \attspan = \postlen$ \\
    \end{itemize}

    On the other hand,
    \begin{itemize}
      \item Let $\attspan < M$.
      \begin{itemize}
        \item If $R < M$, then
      \end{itemize}
      the first post $\postlist\left[1\right]$ is voted
      by all players at round 1 and its score becomes $\playerlen c \left(0.5a +
      b\right)$. Given~(\ref{conv:proof:fewrounds}), all subsequent votes are
      cast with voting power strictly less than 1, thus the last post will have
      a score of $\left(\playerlen - 1\right) c \left(0.5a? + b\right) + c
      \left(\left(0.5 + \epsilon\right)a? + b\right)$ at the end of the
      execution.
      \item If $\attspan = M$,
    \end{itemize}
  \end{itemize}
\end{proof}
